### 2020-04-29 serial.tex
attempting to improve key explanation in Methods

We first begin by describing a general framework for characterizing a distribution of time delays between two epidemiological events;
these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
We can further divide these events into \emph{primary} and \emph{secondary} events.
When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that always or usually occurs before the secondary event ---
most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
% \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative. I'm not saying we should use it here\ldots}
When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
the primary and secondary events are defined in terms of the direction of transmission:
The primary event refers to the event that occurs within an infector and does not necessarily occur before the secondary event.

@@

At the individual-level, both forward and backward \emph{measurements} provide identical measures;
in other words, we can express the total density of primary and secondary events occurring at time $\pt$ and $\st$, respectively, using both forward and backward delay \emph{distributions}:
\begin{equation}
\psize(\pt) f_\pt(\st-\pt) = \ssize(\st) b_\st(\st-\pt),
\end{equation}
where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and secondary cohorts, respectively.
Substituting $\tau = \st - \pt$, it follows that:
\begin{equation}
b_\st(\tau) = \frac{\psize(\st-\tau) f_{\st-\tau}(\tau)}{\ssize(\st)}
\label{eq:backward}
\end{equation}
Therefore, the backward delay distribution depends on the changes in primary cohort size $\tau$ time units ago from the reference time $\st$, $\psize(\st-\tau)$, as well as changes in the forward delay distribution, $f_{\st-\tau}(\tau)$.

>>>>

We first begin by describing a general framework for characterizing a distribution of time delays between two epidemiological events;
these events can be defined either within an infected individual (e.g., infection and symptom onset of an individual, the incubation period) or between infected individuals (e.g., symptom onsets of an infector and an infectee, the serial interval).
We can further divide these events into \emph{primary} and \emph{secondary} events.
When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that always or usually occurs before the secondary event ---
most epidemiological events that can be observed within an individual have clear direction (e.g., infection and onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
% \jd{Rethink, or else rethink ``any'' above: the ``hidden'' time (my term) is the time between onset of infectiousness and onset of symptoms; it is within, but can be positive or negative. I'm not saying we should use it here\ldots}
When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
the primary and secondary events are defined in terms of the direction of transmission:
The primary event refers to the event that occurs within the infector
and does not necessarily occur before the secondary event (which
occurs within the infectee).

@@

\david{deleted ``At the individual-level, both forward and backward
  \emph{measurements} provide identical measures; in other words, we
  can express the total density of primary and secondary events
  occurring at time $\pt$ and $\st$, respectively, using both forward
  and backward delay \emph{distributions}:''}

At the individual level, both forward and backward \emph{perspectives}
must yield identical results (e.g., the length of the incubation
period of a given individual is the same whether measured forward from
the time of infection or backward from time of symptom onset).
Consequently, we must obtain the same number if we count the number of
individuals who became infected at time $\pt$ or the number of
individuals who first showed symptoms at time $\st$; that is, we must
have
\begin{equation}\label{eq:match}
\psize(\pt) f_\pt(\st-\pt) = \ssize(\st) b_\st(\st-\pt),
\end{equation}
where $\mathcal P$ and $\mathcal S$ represent the sizes of primary and
secondary cohorts, respectively.

{\color{red}DE: IN THE MIDST OF EDITING THIS PARAGRAPH... WILL RETURN
  TO THIS, HOPEFULLY LATER THIS EVENING...}

Substituting $\tau = \st - \pt$, it follows that:
\begin{equation}
b_\st(\tau) = \frac{\psize(\st-\tau) f_{\st-\tau}(\tau)}{\ssize(\st)}
\label{eq:backward}
\end{equation}
Therefore, the backward delay distribution depends on the changes in primary cohort size $\tau$ time units ago from the reference time $\st$, $\psize(\st-\tau)$, as well as changes in the forward delay distribution, $f_{\st-\tau}(\tau)$.
